---
title: "AirMoniteringProject"
author: "S18809"
date: "1/23/2024"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tinytex)
```

```{r}
library(tidyverse)
```

```{r}
library(janitor)
```

```{r}
library(skimr)
```

```{r}
library(lubridate)
```

```{r}
library(corrplot)
```


# Load the Data sets for london_local_data

```{r}
col_types <- "cccdddddddd"
air_data <- read_csv(file = "../Data/london_local_data_2022.csv",col_types = col_types)
```

# Find the dimension of the data
```{r}
dim(air_data)
```

```{r}
air_data %>%
  slice_head(n = 6)
```


# Remove the empty rows and cols
```{r}
air_data <- air_data %>%
              remove_empty(c("cols","rows"))
```


```{r}
# skim(air_data)
```

# Find the Summary of the data set
```{r}
summary(air_data)
```

```{r}
glimpse(air_data)
```

# Change the date time in date types
```{r}
air_data <- air_data %>% 
              mutate(date = ymd_hms(date))
```

```{r}
glimpse(air_data)
```

#  Create new columns for date occurrence and time occurrence in the data frame.
```{r}
air_data <- air_data %>%
            mutate(dateOcc = as.Date(date),
            timeOcc = format(date,format = "%H"))
```


```{r}
glimpse(air_data)
```

# Load the date set in local site
```{r}
col_types_s <- "ccddc"
site_data <- read_csv(file = "../Data/london_local_sites.csv",col_types = col_types_s)
```

# Find the dimension of the data
```{r}
dim(site_data)
```
```{r}
site_data %>%
  slice_head(n = 6)
```

```{r}
#skim(site_area)
```


# Find the unique value in site and code
```{r}
length(unique(site_data$site));length(unique(site_data$code))
```

# Find the latitude and longitude in each code
```{r}
site_area <- site_data %>%
  select(code,latitude,longitude)
```


# Find the dimension of site area data set
```{r}
dim(site_area)
```

```{r}
# skim(site_area)
```


# Find the number of unique values for each column in the data set 
```{r}
length(unique(site_area$latitude));length(unique(site_area$code));length(unique(site_area$longitude))
```

# Remove the duplicate values
```{r}
site_area <- distinct(site_area)
```


```{r}
dim(site_area)
```

```{r}
#skim(site_area)
```

# Merge the "air" data frame and the "site_area" data frame in the data set
```{r}
air_data %>%
  slice_head(n = 6)
```

```{r}
site_area %>%
  slice_head(n = 6)
```


```{r}
length(unique(air_data$code))
```

```{r}
air_meta_data <- merge(air_data,site_area,by = "code",all.x = TRUE) 
```


```{r}
#skim(air_meta_data)
```

```{r}
glimpse(air_meta_data)
```
# Find the summary of the data frame "air_meta_data."

```{r}
summary(air_meta_data)
```

# Create the new variable for the month 
```{r}
air_meta_data <- air_meta_data %>%
                 mutate(month = month(dateOcc,label = TRUE))
```

# Convert the time occurrences from 00 to 24 hours.
```{r}
air_meta_data <- air_meta_data %>%
                  mutate(timeOcc = ifelse(timeOcc == "00","24",timeOcc))
```

```{r}
air_meta_data %>%
  slice_head(n = 2)
```
# Create a new data frame for the average measurement of each air gas at each site in London.
```{r}
longitude_data<- air_meta_data %>%
          group_by(longitude) %>%
            summarise(nox = mean(nox,na.rm = TRUE),
            no2  = mean(no2,na.rm = TRUE),
            no = mean(no,na.rm = TRUE),
            pm10 = mean(pm10,na.rm = TRUE),
            o3 = mean(o3,na.rm = TRUE),
            pm2_5 = mean(pm2_5,na.rm = TRUE),
            so2 = mean(so2,na.rm = TRUE))
```

```{r}
#skim(longitude_data)
```

# Replace the null values with zero
```{r}
longitude_data <- replace(longitude_data,is.na(longitude_data),0)
```

```{r}
#skim(longitude_data)
```

# Create the correlation matrix between each variable.
```{r}
cor_matrix<- cor(longitude_data)
```

```{r}
cor_matrix
```
# Draw a corrplot for the above correlation matrix.
```{r}

relation <- corrplot(cor_matrix,
         method = "number",
         tl.col = "black",
         type = "upper")
relation
```

```{r}
postscript(file = "relation.eps",width = 6,height = 4,horizontal = FALSE)
dev.off()
```


```{r}
glimpse(air_meta_data)
```

# Create a new data frame for the sum of spread of all gases in London city.
```{r}
air_gas<- air_meta_data %>%
            summarise(nox = sum(nox,na.rm = TRUE),
            no2 = sum(no2,na.rm = TRUE),
            no = sum(no,na.rm = TRUE),
            pm10 = sum(pm10,na.rm = TRUE),
            o3 = sum(o3,na.rm = TRUE),
            pm2_5 = sum(pm2_5,na.rm = TRUE),
            so2 = sum(so2,na.rm = TRUE))
```


```{r}
air_gas
```


```{r}
colnames(air_gas) <- NULL
measurement <-t(air_gas[, 1:7])
measurement
```
```{r}
# Create the data frame
gases <- c("nox","no2","no","pm10","o3","pm2_5","So2")
 airGas<- data.frame(gases,measurement)
```

```{r}
airGas<- airGas %>%
        mutate(percent = round(measurement/sum(measurement) * 100,digits = 2))
```


```{r}
airGas
```


```{r}
# Draw the Bar Chart For all gases spread within year
airGas %>%
  ggplot(mapping = aes(x = gases, y = percent, fill = gases)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(percent, "%")),
            position = position_stack(vjust = 0.5),
            size = 3, color = "black") +
  theme_minimal() +
  ggtitle("Gas Percentages in London Over the Year") +
  theme(
    plot.title = element_text(hjust = 0.5, vjust = 0.1),
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels for better readability
  )
```

#Create a new data frame for the average values of each air pollutant based on the month in London local sites.
```{r}
glimpse(air_meta_data)
```


```{r}
air_mean_data<- air_meta_data %>%
                  group_by(month) %>%
                  summarise(nox = mean(nox,na.rm = TRUE),
                  no2  = mean(no2,na.rm = TRUE),
                  no = mean(no,na.rm = TRUE),
                  pm10 = mean(pm10,na.rm = TRUE),
                  o3 = mean(o3,na.rm = TRUE),
                  pm2_5 = mean(pm2_5,na.rm = TRUE),
                  so2 = mean(so2,na.rm = TRUE)
            )
```


```{r}
air_mean_data
```
# Draw a line chart for the average measurement of each gas based on each month in London.
```{r}
air_mean_data %>% 
  ggplot(mapping = aes(x = month,group = 1))+
  geom_line(aes(y = nox,color = "nox"))+
  geom_line(aes(y = no2,color = "no2"))+
  geom_line(aes(y = no,color = "no"))+
  geom_line(aes(y = pm10,color = "pm10"))+
  geom_line(aes(y = o3,color = "o3"))+
  geom_line(aes(y = pm2_5,color = "pm2_5"))+
  geom_line(aes(y = so2,color = "so2"))+
  theme_minimal()+
  scale_color_manual(values = c("nox" = "green",
                                "no2" = "red",
                                "no" = "blue",
                                "pm10" = "yellow",
                                "o3" = "orange",
                                "pm2_5" = "purple",
                                "so2" = "black"), name = "AirGases")+
  ggtitle("Line chart for Average air measurment for each gases")+
  ylab("Average")
```

# Find the average value for each gas based on each local site.
```{r}
 air_meta_data %>%
  group_by(code) %>%
  summarise(nox = mean(nox,na.rm = TRUE),
  no2  = mean(no2,na.rm = TRUE),
  no = mean(no,na.rm = TRUE),
  pm10 = mean(pm10,na.rm = TRUE),
  o3 = mean(o3,na.rm = TRUE),
  pm2_5 = mean(pm2_5,na.rm = TRUE),
  so2 = mean(so2,na.rm = TRUE))
```

# Create a data frame for the nitrogen group in local sites.
```{r}
nitrogen_group <- air_meta_data %>%
  select(site,code,nox,no2,no,date,timeOcc,month)
```


```{r}
#skim(nitrogen_group)
```

# Find the summary statistics for the nitrogen group.
```{r}
summary(nitrogen_group)
```

# Remove the null values from data frame.
```{r}
nitrogen_group <- nitrogen_group %>%
                  drop_na()
```


```{r}
#skim(nitrogen_group)
```

```{r}
glimpse(nitrogen_group)
```

# Calculate the average measurement for nitrogen oxide (NOx) and identify the maximum measurement for each month with  for site.

```{r}
nitrogen_group %>%
  group_by(month,code) %>%
  summarise(Avg_nox = mean(nox)) %>%
  arrange(desc(Avg_nox)) %>%
  slice(1)
```
# Add a new variable 'weeks' to the data frame
```{r}
nitrogen_group <-  nitrogen_group %>%
                      mutate(weeks = weekdays(date))
```


# Draw boxplots for air measurements in January, August, September, October, November, and December at sites EA6, LB4, and LW4 based on weeks
```{r}
nitrogen_group %>%
  filter(code %in% c("EA6","LB4","LW4"),
         month %in% c("Jan","Aug","Sep","Oct","Nov","Dec")) %>%
  group_by(weeks) %>%
  ggplot(mapping = aes(x = weeks,y = nox,fill = code)) +
  geom_boxplot()+
  scale_fill_discrete("code",label = c("EA6" = "Ealing - Hanger Lane Gyratory","LB4" = "Lambeth - Brixton Road","LW4" = "Lewisham - Loampit Vale"))+
  ggtitle("Box plot for  measurement vs weeksdays in nox in 3 sites")+
  ylab("Measurement")
```


```{r}
nitrogen_group %>%
  slice_head(n = 2)
```


# Draw a scatter plot for the average measurement of nitrogen oxide on Thursday and Friday in January and October based on hours.
```{r}
nitrogen_group %>%
  filter(month %in% c("Jan","Oct"),
         weeks %in% c("Thursday","Friday")) %>%
  group_by(timeOcc,weeks) %>%
  summarise(avg_nox = mean(nox)) %>%
  ggplot(mapping = aes(x = timeOcc, y = avg_nox,color = weeks)) +
  geom_point()+
  labs(title = "Average NOx by Time Occurrence and Weekday(Thursday & Friday)",
       x = "Time Occurrence", y = "Average NOx",
       color = "Weekday") +
  theme_minimal()
```

# Find the maximum measurement of nitrogen dioxide in areas with high dispersion in January, March, and December.
```{r}
nitrogen_group %>%
  filter(month %in% c("Jan","Mar","Dec")) %>%
  group_by(month,code) %>%
  summarise(avg_no2 = mean(no2)) %>%
  arrange(desc(avg_no2)) %>%
  slice(1)
```

# Find the maximum measurement of Nitric Oxide in areas with high dispersion in January and December
```{r}
nitrogen_group %>%
  filter(month %in% c("Jan","Dec")) %>%
  group_by(month,code) %>%
  summarise(avg_no = mean(no)) %>%
  arrange(desc(avg_no)) %>%
  slice(1)
```
# Find the minimum measurement of Nitric Oxide in areas with high dispersion in January and December
```{r}
nitrogen_group %>%
  filter(month %in% c("Jan","Dec")) %>%
  group_by(month,code) %>%
  summarise(avg_no = mean(no)) %>%
  arrange(avg_no) %>%
  slice(1)
```
# Determine the Trend for nitrogen gases for each site
```{r}

nitrogen_group %>%
  group_by(code) %>%
  summarise(avg_nox = mean(nox),
            avg_no2 = mean(no2),
            avg_no = mean(no)) %>%
  ggplot(aes(x = code,group = 1)) +
  geom_line(aes(y = avg_nox , color = "nox"))+
  geom_line(aes(y = avg_no , color = "no"))+
  geom_line(aes(y = avg_no2 , color = "no2"))+
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5)
  )+
  ggtitle("Line chart for trend in nitrogen group in each code")+
  ylab("Average Measurement")+
  scale_color_manual(values = c("nox" = "Red",
                                "no" = "Blue",
                                "no2" = "Green"),name = "nitrogen_gases")
  
```

```{r}
glimpse(air_meta_data)
```

# Create a new data frame for the ocean gas
```{r}
ocen_group <- air_meta_data %>%
  select(code,dateOcc,timeOcc,o3,month)
```

```{r}
#skim(ocen_group)
```

# Remove the null values
```{r}
ocen_group <- ocen_group %>%
  drop_na()
```

# Create a new variable for weeks in the ocean group data frame
```{r}
ocen_group <- ocen_group %>%
              mutate(weeks = weekdays(dateOcc))
```

```{r}
head(ocen_group,2)
```

# Find the maximum measurement of ocen gas in areas with high dispersion in Febuary,April and Augest.
```{r}
ocen_group %>%
  filter(month %in% c("Feb","Apr","Aug")) %>%
  group_by(month,code) %>%
  summarise(avg_o3 = mean(o3)) %>%
  arrange(desc(avg_o3)) %>%
  slice(1)
```
# Determine which area has the maximum amount of O3 spread.
```{r}
ocen_group %>%
  filter(o3 == max(o3))
```

# Calculate the weekly spread of ozone in Richmond Upon Thames - Barnes Wetlands
```{r}
weeks_mesure_o3<- ocen_group %>% 
                      filter(code == "RI2") %>%
                      group_by(weeks) %>%
                      summarise(measurement = sum(o3))

```


```{r}
weeks_mesure_o3
```

# Add a new variable for percentage columns in each days
```{r}
weeks_mesure_o3 <- weeks_mesure_o3 %>%
                  mutate(percentage = round((measurement*100/sum(measurement)),digits = 2))

```

# Draw the pie chart for ozone measurements each week in Richmond Upon Thames - Barnes Wetlands
```{r}
weeks_mesure_o3 %>%
  ggplot(mapping = aes(x = " ", y = measurement,fill = weeks))+
  geom_bar(stat = "identity", width = 1,show.legend = FALSE) +
  coord_polar(theta = "y")+
  geom_text(aes(label = paste0(weeks, "\n", percentage, "%")), position = position_stack(vjust = 0.5)) +
  theme_void()+
  ggtitle("Pie chart for ozone (O3) measurements each week in \n Richmond Upon Thames - Barnes Wetlands")+
  theme(
    plot.title = element_text(hjust = 0.5,vjust = 0.1)
  )
  
```

```{r}
ocen_group %>%
  slice_head(n = 2)
```


# Find the trends for hourly measurements on Satuday in Richmond Upon Thames - Barnes Wetlands.
```{r}
ocen_group %>%
  filter(code == "RI2",weeks == "Saturday") %>%
  group_by(timeOcc) %>%
  summarise(avg = mean(o3)) %>%
  ggplot(aes(x = timeOcc,y = avg,group = 1)) +
  geom_line(aes(color = "ozone"),size = 1.2)+
  labs(title =  "Average Ozone Levels over Time \n (Location: Richmond Upon Thames - Barnes Wetlands, Saturday)",
       x = "Time Occurance",
       y = "Ozone Levels")+
  scale_color_manual(values = c("ozone" = "red"),name = "Air Gas")
```


```{r}
glimpse(air_meta_data)
```
# Create the new data frame for pm_10 gas measurement in London sity
```{r}
pm_10 <- air_meta_data %>%
  select(code,month,pm10)
```

# Remove the null values
```{r}
pm_10 <- pm_10 %>%
  drop_na()
```

```{r}
#skim(pm10)
```

# Find the areas with the spread of PM_10 in London within one year.
```{r}
pm_10 %>%
  group_by(code) %>%
  summarise(measurement = sum(pm10)) %>%
  arrange(desc(measurement))
```

# Find the top 5 areas with the maximum spread of PM10 in London within one year

```{r}
pm_10 %>%
  group_by(code) %>%
  summarise(measurement = sum(pm10)) %>%
  slice_max(measurement,n = 5)
```


# Draw a bar chart for the spread levels of PM10 in the top 5 areas, organized by month.
```{r}
pm_10 %>%
  filter(code %in% c("LB5","EI1","HS8","WAA","LW4")) %>%
  group_by(month,code) %>%
  summarise(measurement = sum(pm10)) %>%
  ggplot(aes(x = month,y = measurement,fill = code)) +
  geom_bar(stat = "identity",position = "dodge")+
  scale_fill_discrete("Sites",label = c("LB5" = "Lambeth - Bondway Interchange",
                                        "EI1" = "Ealing - Western Avenue",
                                        "HS8" = "Hounslow Gunnersbury",
                                        "WAA" = "Wandsworth - Battersea",
                                        "LW4" = "Lewisham - Loampit Vale"))+
  ggtitle("Barplot pm_10 for top 5 sites")
```



```{r}
glimpse(air_meta_data)
```

# Create the new  data frame for measurement in pm2_5 gas 
```{r}
pm_2.5 <- air_meta_data %>%
  select(site,code,dateOcc,timeOcc,month,pm2_5)
```


```{r}
#skim(pm_2.5)
```

# Remove the null values
```{r}
pm_2.5 <- pm_2.5 %>%
  drop_na()
```

# Find the maximum average measurement of pm_2.5 in areas with high dispersion in month

```{r}
unique(pm_2.5$code)
```


```{r}
pm_2.5 %>%
  group_by(code,month) %>%
  summarise(avg_measure = mean(pm2_5)) %>%
  arrange(desc(avg_measure)) %>%
  slice(1)
```

```{r}
# Identify the trend for pm2_5 gases on January and March in 3 sites
pm_2.5 %>%
  filter(month %in% c("Jan","Mar")) %>%
  mutate(weeks = weekdays(dateOcc)) %>% # Create the variables for weeks
  group_by(weeks,code) %>%
  ggplot(aes(x = weeks , y = pm2_5,fill = code))+
  geom_boxplot()+
  scale_fill_discrete("code",label = c("HK6" = "Hackney - Old Street",
                                       "HS4" = "Hounslow Chiswick",
                                       "WMD" = "Westminster - Elizabeth Bridge"))+
  ggtitle("Box plot for pm2_5 air gases in each day")
```


```{r}
# Create the line chart for measure level in pm2_5 on Tuesday
pm_2.5 %>%
 mutate(weeks = weekdays(dateOcc)) %>% # Create the variables for weeks
  filter(weeks == "Tuesday") %>% 
  group_by(timeOcc) %>%
  summarise(avg_pm25 = mean(pm2_5)) %>%
  ggplot(aes(x = timeOcc , y = avg_pm25 , group = 1))+
  geom_line()+
  ggtitle("Line chart for average measurement level in Tuesday")+
  ylab("pm2_5")+
  xlab("hours")
  
```



```{r}
glimpse(air_meta_data)
```

# Create the new data frame for measurement of so2 gas in London
```{r}
so_2 <- air_meta_data %>%
  select(code,so2,dateOcc,month)
```

# Remove the null values
```{r}
so_2 <- so_2 %>%
  drop_na()
```


```{r}
summary(so_2)
```
# Find the site in London where the SO2 gas has disappeared.
```{r}
so_2 %>%
  group_by(code) %>%
  summarise(measure = sum(so2)) 
```
# Draw a line chart to illustrate the spread of SO2 levels each month in Lambeth - Bondway Interchange
```{r}
so_2 %>%
  group_by(code,month) %>%
  summarise(measure = sum(so2)) %>%
  ggplot(mapping = aes(x = month, y = measure,group = 1))+
  geom_line(aes(color = code))
```

# Check whether there are any streets where all gases have spread
```{r}
air_meta_data[complete.cases(air_meta_data),]
```

# Check whether there are any streets where all gases have spread without so2 gas
```{r}
air_meta_data %>%
  select(code,no2,nox,no,pm10,o3,pm2_5) %>%
  drop_na() %>%
  group_by(code) %>%
  summarise(nox = mean(nox),
            no2 = mean(no2),
            no = mean(no),
            pm10 = mean(pm10),
            o3 = mean(o3),
            pm2_5 = mean(pm2_5))
```
# Calculate the average measurement for each gas in Lambeth - Bondway Interchange.
```{r}
air_meta_data %>%
  filter(code == "LB5") %>%
  group_by(code) %>%
  summarise(nox = mean(nox,na.rm = TRUE),
            no2 = mean(no2,na.rm = TRUE),
            no = mean(no,na.rm = TRUE),
            pm10 = mean(pm10,na.rm = TRUE),
            o3 = mean(o3,na.rm = TRUE),
            pm2_5 = mean(pm2_5,na.rm = TRUE),
            so2 = mean(so2,na.rm = TRUE))
```


